\documentclass[a4paper,10pt,oneside, fleqn]{article}
% Druckbereich: \areaset[BCOR]{textwidth}{textheight}
% BCOR ist "Binding Correction", also wieviel Innenrand verloren geht
% A4 hat 297mm x 210mm
% wenn keine Marginalien, dann ist Breite 15cm vielleicht besser
%\areaset[0cm]{15cm}{25cm}


\usepackage[english,mt]{ethidsc}    % deutsche Übersetzungen und Wortumbrüche
\usepackage{mcode}
\usepackage{subfigure}

   
% Page header (don't change)____________________________________________________
\setlength{\parindent}{0em}                 % Disable parindent
\rhead[\nouppercase{\rightmark}]{\thepage}  % Special headings
\lhead[\thepage]{\nouppercase{\leftmark}}   % Special headings
\cfoot{} 
 
%%% hier können noch viel viel mehr Einstellungen kommen

%%% Title page
\title{Using Fast Fourier Transformation to Suppress Spiders in Astronomical Data}

\studentA{Jennifer Studer}
\ethidA{16-915-928}
\semesterA{2}
\emailA{studerje@student.ethz.ch}

\supervision{Hans Martin Schmid\\ Christian Tschudi}
\date{\today}

 
%%%% hier beginnt der Inhalt %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

\maketitle

\pagestyle{fancy}               	% Fancy headings
\pagenumbering{arabic}

\vspace*{\fill}
\begin{abstract}
To suppress the spiders in astronomical data we use Fourier theory. We first transform the image data to the $r$-$\varphi$ plane so that the spiders are parallel to each other. Then we simulate the spiders to investigate the frequency space of spiders only. With the knowledge gained by the simulations we suppress some specific patterns in the frequency plane of the image data which are caused by the spiders and then transform the result back into the image plane. We receive an image where the spiders are slightly suppressed. 
\end{abstract}
\vspace*{\fill}
\newpage

\tableofcontents
\newpage

\input{text/introduction.tex}
\input{text/aperture_photometry.tex}
\input{text/interpolation.tex}
\input{text/radial_intensity.tex}
\input{text/fourier.tex}
\input{text/suppression.tex}
\input{text/conclusion.tex}


\section{Acknowledgments}
I (Jennifer Studer) want to thank Hans Martin Schmid for is help and support I got from him during the entire project and the interesting conversation we had. For the supervision I want to thank Hans Martin Schmid and Christian Tschudi. I also want to thank Kaya Ercihan and Tanja Finger for proofreading parts of my thesis. 

\newpage 

\appendix
\input{text/append_FFT_almostPer.tex}

\newpage
\bibliographystyle{plain}
\bibliography{bib_exo}

\end{document}
